Digital History in Finland, 1488-1828

### 2016-07-07 inst/examples/manuscript-krakow.Rmd
updated manuscript file to deduplicated data

# Define time span
min.year <- 1488
max.year <- 1828

@@

```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=12}
theme_set(theme_bw(20))
ntop = 10
p <- top_plot(fen, "publication_place", ntop = ntop)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places\n(Fennica)")
pf = p

theme_set(theme_bw(30))
p <- top_plot(kun, "publication_place", ntop = ntop)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places\n(Kungliga)")
pk = p

@@

Focus on Gävle (gray) during riksdagar. Gävle has `r sum("Gävle" %in% fen$publication_place)` occurrences in Fennica, hence not included here. The figure on Gävle is based on Kungliga.

@@

```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
tops <-  names(top(fen, "publisher", 5))

@@

```{r topics2.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
tops <-  names(top(fen, "publisher", 5))

@@

```{r topics3.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
tops <-  names(top(fen, "publisher", 5))

@@

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
df <- fen %>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

The raw data contains metadata `r nrow(fenraw)` and `r nrow(kunraw)` documents in Fennica and Kungliga, respectively. We limited the present analysis in the time interval `r min(df0$publication_year)`-`r max(df0$publication_year)`, yielding a subset of `r nrow(subset(df0, catalog == "Fennica"))` (`r round(100*nrow(subset(df0, catalog == "Fennica"))/nrow(fenraw), 1)`%) and `r nrow(subset(df0, catalog == "Kungliga"))` (`r round(100*nrow(subset(df0, catalog == "Kunliga"))/nrow(kunraw), 1)`%) documents for Fennica and Kungliga, respectively.

@@

```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=20, out.width="850px"}
theme_set(theme_bw(10))
dfs <- fen %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors\n(Fennica)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pf = p

theme_set(theme_bw(20))
dfs <- kun %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors\n(Kungliga)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pk = p

>>>>

# Define time span
min.year <- 1488
max.year <- 1828
output.folder <- "output.tables"

@@

```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=12}
theme_set(theme_bw(20))
ntop = 10
p <- top_plot(subset(df0, catalog == "Fennica"), "publication_place", ntop = ntop)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places\n(Fennica)")
pf = p

theme_set(theme_bw(30))
p <- top_plot(subset(df0, catalog == "Kungliga"), "publication_place", ntop = ntop)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places\n(Kungliga)")
pk = p

@@

Focus on Gävle (gray) during riksdagar. Gävle has `r sum("Gävle" %in% subset(df0, catalog == "Fennica")$publication_place)` occurrences in Fennica, hence not included here. The figure on Gävle is based on Kungliga.

@@

```{r topics.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
tops <-  names(top(subset(df0, catalog == "Fennica"), "publisher", 5))

@@

```{r topics2.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
tops <-  names(top(subset(df0, catalog == "Fennica"), "publisher", 5))

@@

```{r topics3.per.publisher, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6, out.width="430px", fig.show="hold"}
tops <-  names(top(subset(df0, catalog == "Fennica"), "publisher", 5))

@@

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=7, fig.width=10, fig.show="hold", out.width="430px"}
df <- df0 %>%
      filter(catalog == "Fennica") %>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

The raw data contains metadata `r nrow(subset(df.full, catalog == "Fennica"))` and `r nrow(subset(df.full, catalog == "Kungliga"))` documents in Fennica and Kungliga, respectively. We limited the present analysis in the time interval `r min(df0$publication_year)`-`r max(df0$publication_year)`, yielding a subset of `r nrow(subset(df0, catalog == "Fennica"))` (`r round(100*nrow(subset(df0, catalog == "Fennica"))/nrow(subset(df.full, catalog == "Fennica")), 1)`%) and `r nrow(subset(df0, catalog == "Kungliga"))` (`r round(100*nrow(subset(df0, catalog == "Kunliga"))/nrow(subset(df.full, catalog == "Kungliga")), 1)`%) documents for Fennica and Kungliga, respectively.

@@

```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=20, out.width="850px"}
theme_set(theme_bw(10))
dfs <- df0 %>%
  filter(catalog == "Fennica") %>%
  filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors\n(Fennica)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pf = p

theme_set(theme_bw(20))
dfs <- df0 %>%
  filter(catalog == "Kungliga") %>%
  filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors\n(Kungliga)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pk = p
